---
title: "R Markdown Document"
output: html_document
---

## Introduction

This is an *R Markdown Document*. R Markdown Documents are written in a language called *R Markdown*. We will take a closer look at R Markdown today.

An *R Markdown Document* is sort of an electronic lab notebook, but for data analysis. You will use R Markdown Documents to: 

- write *narrative* about your data analysis in plain English -- e.g. explain your experimental design or write down the interpretation of a graphical plot;
- write *code* in R; and
- see the *results* of the R code after it's been run, e.g. a graphical plot or a table.

You can turn an R Markdown Document into an attractively formatted *HTML* document. This is called *rendering* or *knitting*. Click the *Knit* button on the top of this window to try it now. Take a look at how the document that appears compares with the plain text here. (You may then close the browser window that will open up.)


## Editing R Markdown

If you are reading this, you are most likely using the *RStudio Editor* at the moment. The RStudio Editor makes it easy to create and edit R Markdown Documents.

Adding narrative is simple: just use the mouse or the keyboard to move the cursor to the place where you want to make a change, and then add or change the text. For practice, edit the following line to replace *XXX* below with your name:


  My name is *XXX*, and I'm editing an R Markdown Document!


Great! Now hit *Preview* again and see if you can the change you just made in the rendered HTML document.


## Code Chunks

In an R Markdown document, R code goes into *code chunks*. 

Each code chunk 

- starts with three back-ticks ``` and the letter "r" in curly brackets {}. (On your keyboard, the back-tick is usually located directly below your Escape key). 
- ends with a line that has three backticks and nothing else. 
- has any number of lines of R code in between these two features.

See, for example, here:

```{r}
# R code goes here
```

As you can see directly above, code chunks have a gray background in the RStudio editor. This way it's easy to see where all the code chunks are in your R Markdown Document. 


## Running code chunks

You can *run the code* in a code chunk by clicking the *green triangle/play-button* in the upper right corner of the code chunk. The results will appear beneath the chunk. Try running the code chunk below now!

```{r}
plot(cars)
```

If you can see a scatterplot - good job!

Click *knit* again to see how the graphical plot will look like in the knitted document!

## More code chunks

Your turn now: try writing a code chunk. The code chunk should run only the following command: 

plot(pressure)




